Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-05-06 review/review_response.md

--------------
Minor critiques
--------------

page 1, column 1
line 55: "host stars age" -> "host stars' age"
**Resolved**

page 2, column 1
line 15: "While several works found similar properties on the two populations, like a similar densities" -> "While several works found similar properties for the two populations, like similar [mass? number?] densities"

page 2, column 2
line 38: "detected in the extreme V-K colour indexes (>7.8)." -> "based on the extreme V-K colours (>7.8) of the companions."
**Changed**

@@

page 5, column 1
line 51: what is "I_space"? should this be "I_star"?  
**YES**

page 5, column 2
move section 3.2 to be before 3.1.3 since you describe how Tapas is used here

page 8, column 2
line 44: "radii radii" -> "radii"

page 9, column 1
line 13: "For each model we further allow the continuum level to be varied by ±0.05 as a free parameter" - is this additive or multiplicative?
**Multiplicative scaling.
I have changed the line to thus read -
"For each model we further allow the continuum level to be scaled between 0.95 and 1.05 as a free parameter taking ..."**

### 2019-05-06 nir_companions.tex
fix units on gamma in table 2
v band extremes fix
multiplicative scaling fix

\textit{K}-band spectra were obtained with the goal to achieve a direct detection of the companion spectra through the application of a spectral-differential approach. Doing so would enable a further constraint to be placed on their masses. The \textit{K}-band is used to achieve a high contrast relative to the host star, detected in the extreme V-K colour indexes (>7.8).

@@

\subsection{\texorpdfstring{\(\chi^{2}\)}\ \ method}
\label{subsec:chi2}
The well known \(\chi^{2}\) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters. The \(\chi^{2}\) is defined as
\begin{equation}
\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\sigma}_{i}\,,
\end{equation}
  where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator. {This method estimates the spectral noise using numerical derivatives of the spectra. We followed the procedure outlined in~\citet{czesla_posteriori_2018}, analysing the results from successive parameter combinations to settle on an order of approximation (derivative level) of 5, and a jump parameter (pixels skipped to avoid correlations) of 2.} We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500, {similar to the values given in Table~\ref{tab:observations} calculated from the continuum of detector 2.}

@@

For each model we further allow the continuum level to be varied by \(\pm 0.05\) as a free parameter taking the model with the smallest \(\chi^2\) value.

>>>>

\textit{K}-band spectra were obtained with the goal to achieve a direct detection of the companion spectra through the application of a spectral-differential approach. Doing so would enable a further constraint to be placed on their masses. The \textit{K}-band is used to achieve a high contrast relative to the host star, {\bl based on the} extreme V-K colour indexes (>7.8) {\bl of the companions}.

@@

\subsection{\texorpdfstring{\(\chi^{2}\)}\ \ method}
\label{subsec:chi2}
The well known \(\chi^{2}\) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters. The \(\chi^{2}\) is defined as
\begin{equation}
\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\bl {\sigma}_{i}^{2}}\,,
\end{equation}
  where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator. {This method estimates the spectral noise using numerical derivatives of the spectra. We followed the procedure outlined in~\citet{czesla_posteriori_2018}, analysing the results from successive parameter combinations to settle on an order of approximation (derivative level) of 5, and a jump parameter (pixels skipped to avoid correlations) of 2.} We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500, {similar to the values given in Table~\ref{tab:observations} calculated from the continuum of detector 2.}

@@

For each model we further allow the continuum level to be {\bl scaled between 0.95 and 1.05 as a free parameter} taking the model with the smallest \(\chi^2\) value.
